Response to Pachter’s Review

### 2020-01-23 index.Rmd
one more figure

@@

@@

We have debunked the claim that age is the greatest contributor for the difference in citations and citations per year between signers of Letter A, B, and C. Indeed, the least meritorious of mathematicians as a whole signed letter A, whereas the more meritorious signed letters B and C, with merit judged by citations. If one was not willing to believe citations impose even a small order on merit, one could replace citations with Fields medals, AMS Fellowships, or many other metrics. One could make extrapolations by coupling this analysis with work by Topaz, but we refrain from doing so.

>>>>

Last Update: January 23rd 2:50 A.M.

@@

Perhaps removing Lior was a confounder. So we remove the top five mathematicians from C.

```{r, echo = FALSE}
x.youngest.age <- 15
x.oldest.age <-65
x.age.range <- x.youngest.age:x.oldest.age
year.span <- x.oldest.age - x.youngest.age
x.a <- vector(mode="numeric", length=year.span)
x.b <- vector(mode="numeric", length=year.span)
x.c <- vector(mode="numeric", length=year.span)

a.trim <- tail(sort(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&(age < 100)))$citations),1)
c.trim <- tail(sort(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&(age < 100)))$citations),5)
df.a.trimmed <- subset(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&(age < 100)&(!is.na(citations))&!(citations %in% a.trim)))
df.c.trimmed <- subset(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&(age < 100)&(!is.na(citations))&!(citations %in% c.trim)))

plot(x.age.range,x.c,
  type="l",
  col="chartreuse3",
  ylim=c(0,7000),
  main="Average citations of Professors as a function of age \n (Lior Pachter Removed, \n and 5 highest cited of Letter C removed)",
  ylab="mean citations",
  xlab="PhD age",
  lwd=2)
lines(x.age.range,x.a,
  type="l",
  col="red",
  lwd=2)
legend("topleft",
  c("Letter A","Letter C"),
  fill=c("red","chartreuse3"))
```

@@

We have debunked the claim that age is the greatest contributor for the difference in citations and citations per year between signers of Letter A, B, and C. Indeed, the least meritorious of mathematicians as a whole signed letter A, whereas the more meritorious signed letters B and C, with merit judged by citations. If one was not willing to believe citations impose even a small order on merit, one could replace citations with Fields medals, AMS Fellowships, or many other metrics.
